TODO: title

### 2014-04-24 paper/main.tex
done with results, figures tenatively added, after next run will commit images and redirect

\subsection{Prediction accuracy}
  % Prediction accuracy
    % RMSE plot

TODO: rmse plot

    % point out error bars etc.
    % explain / interpret plot
  Figure \ref{fig:rmse} shows how accurate our algorithms are as measured by RMSE.
  As would be expected the accuracy of our item baseline doesn't change as the amount of information changes.
  The User-User and svd algorithms both perform as expected, starting out with the same accuracy as the item baseline, and then monotonically improving.
  User-User does show a small increase of error with only one rating, but the change is quite small and unlikely to be noticed by users.
  Interestingly, User-User and svd both perform about as well as our smarter user item baseline. %TODO: explain this better

@@

@@

  % TopN average rating / topn rmse
    % interpret graph and reason about what it means about quality
  The first graph in figure \ref{fig:topN.rmse} shows the average number of items in the top 20 recommendations for each algorithm that were also in the test set.
  The average number of test set items in recommendations shows a similar trend to the MAP, precision, and recall metrics, user-user getting by far the fewest seen items, and the baseline getting the most.
  %TODO: talk about trust building here!

@@

\subsection{Other recommender metrics}
  % Other recommender metrics
    % popularity graph
  The first graph in figure \ref{fig:pop} shows the average popularity of recommended items by each algorithm.
  %TODO: re-write this
  Across all datapoint sizes the ranking of algorithms is the same, with the baselines recommending the most popular movies, followed by svd, which recommends less popular movies, then Item-Item, which recommends much less popular movies, leaving User-User to recommend the least popular movies.
  Unfortunately, we don't know of any guideline for understanding how popular users desire their recommendations to be.
  That in mind, we expect that users will feel the baseline's popularity (around 1000) is too high, and User-User's popularity (around 50) is too low.
  SVD and Item-Item both seem to perform well, with SVD generating more popular recommendations, than Item-Item, and both algorithms showing a significant trend to make less popular predictions as we know more about the user.

@@

>>>>

\subsection{Prediction accuracy}
  % Prediction accuracy
\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{/export/scratch/kluver/workspace/coldstartrecommendation/lenskit/output/ekstrandTuning/accuracy.pdf}
  \caption{TODO}
  \label{fig:rmse}
  \label{fig:ndcg}
\end{figure*}
    % RMSE plot
    % point out error bars etc.
    % explain / interpret plot
  Figure \ref{fig:rmse} shows how accurate our algorithms are as measured by RMSE.
  As would be expected the accuracy of our item baseline doesn't change as the amount of information changes.
  The User-User and svd algorithms both perform as expected, starting out with the same accuracy as the item baseline, and then monotonically improving.
  User-User does show a small increase of error with only one rating, but the change is quite small and unlikely to be noticed by users.
  Interestingly, User-User and svd both perform about as well as our smarter user item baseline. %TODO: explain this better

@@

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=1.1\linewidth]{/export/scratch/kluver/workspace/coldstartrecommendation/lenskit/output/ekstrandTuning/TopNPrecision.pdf}
  \caption{TODO}
  \label{fig:map}
\end{figure*}

@@

  % TopN average rating / topn rmse
    % interpret graph and reason about what it means about quality

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=1.1\linewidth]{/export/scratch/kluver/workspace/coldstartrecommendation/lenskit/output/ekstrandTuning/rmse_20.pdf}
  \caption{TODO}
  \label{fig:topN.rmse}
\end{figure*}

  The first graph in figure \ref{fig:topN.rmse} shows the average number of items in the top 20 recommendations for each algorithm that were also in the test set.
  The average number of test set items in recommendations shows a similar trend to the MAP, precision, and recall metrics, user-user getting by far the fewest seen items, and the baseline getting the most.
  %TODO: talk about trust building here!

@@

\subsection{Other recommender metrics}
  % Other recommender metrics

\begin{figure*}[ht!]
  \centering
  \includegraphics[width=\linewidth]{/export/scratch/kluver/workspace/coldstartrecommendation/lenskit/output/ekstrandTuning/popdiv.pdf}
  \caption{TODO}
  \label{fig:pop}
\end{figure*}

    % popularity graph
  The first graph in figure \ref{fig:pop} shows the average popularity of recommended items by each algorithm.
  %TODO: re-write this
  Across all datapoint sizes the ranking of algorithms is the same, with the baselines recommending the most popular movies, followed by svd, which recommends less popular movies, then Item-Item, which recommends much less popular movies, leaving User-User to recommend the least popular movies.
  Unfortunately, we don't know of any guideline for understanding how popular users desire their recommendations to be.
  That in mind, we expect that users will feel the baseline's popularity (around 1000) is too high, and User-User's popularity (around 50) is too low.
  SVD and Item-Item both seem to perform well, with SVD generating more popular recommendations, than Item-Item, and both algorithms showing a significant trend to make less popular predictions as we know more about the user.

@@

\begin{figure}[ht!]
  \centering
  \includegraphics[width=1.1\columnwidth]{/export/scratch/kluver/workspace/coldstartrecommendation/lenskit/output/ekstrandTuning/topN_entropy.pdf}
  \caption{TODO}
  \label{fig:spread}
\end{figure}
